Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-11-20 Cost_manuscript.Rmd
adding clinical details

  Our findings provided partial support for our pre-registered hypotheses( https://osf.io/2rsgm/registrations). In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points. This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013]. This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [@Cash-Padgett2020; @Garrett2020; @Dundon2020]. In contrast, our prediction that effort requirements would produce more acceptances only held for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment. These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; @Olivola2013]. Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands. The fact that predicted stable preferences for cognitive effort carried over onto the beginning of the within-subjects experiment further supported a task-specific modulation. However, the unexpected gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.

@@

  It is possible that participants gravitated towards cognitive demands because the task configuration was not effortful. This could be due to differences in how we calibrated cognitive and physical tasks. For physical demands, we adjusted the gripping threshold to people's maximum strength, whereas we trained participants in the cognitive tasks until they reached criterion. Training might have improved response automaticity and reduce error-related risk. In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [ivan; eisenberger]. Even so, we believe our manipulations were successful in inducing feelings of effort. Hand grips are regularly used to probe physical effort [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to feel cognitively effortful by recruiting cognitive control [@Kool2010; @Shenhav2017]. Furthermore, we observed a steeper decrease in acceptances over time at longer handling times, a hallmark of effortful exhertion [@Treadway2009].

@@

  advancing the field: rather than purely framing effort and delay as costs, here we let people decide what they prefer, and wrap it in a computational framework that tells us when costs are actually valuable. 
### *Points to cover*

@@

- Clinical: such deviations in the willingness to pursue effort can predict depression relapse (https://jamanetwork.com/journals/jamapsychiatry/article-abstract/2761562), and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia (https://www.researchgate.net/publication/337361164_Pathways_to_Motivational_Impairments_in_Psychopathology_Common_Versus_Unique_Elements_Across_Domains). Like, the aversion is due to focusing on different elements of the task. Excessive aversion to delay and effort can manifest as impulsivity and apathy, respectively [1,10–12], fluctuations in which are hallmark symptoms of various mental illnesses and substance use disorders [13]. Our findings promote the idea that motivation to exhert effort can be boosted by chopping tasks into smaller digestible chunks that don't make them feel as long. Rather than telling them the final goal, keep them busy (this should be already a thing, I'm sure...). The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler). This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.

>>>>

  Our findings provided partial support for our pre-registered hypotheses (https://osf.io/2rsgm/registrations). In accord with our predictions, decision makers in both experiments successfully approximated reward-maximizing strategies, as evidenced by acceptance rates near optimal points. This is in line with previous foraging experiments, where the main deviation from optimality has been a tendency to overharvest [@Constantino2015; @Wikenheiser2013]. This successful integration of the task was further evidenced by the ability of individuals to describe near-optimal strategies after participation, discarding the possibility of our results being driven by noise or bias in the estimation of environmental richness [@Cash-Padgett2020; @Garrett2020; @Dundon2020]. In contrast, our prediction that effort requirements would produce more acceptances only held for the cognitive group, and this tendency for higher acceptances did not switch to passive waiting as predicted for the within-subjects experiment. These hypotheses originally stemmed from prevalent proposals that incentivized work should become more appealing [@Eisenberger1992; @Inzlicht2018], but that people would opt for the easiest available way to achieve desired outcomes [@Hull1943; @Olivola2013]. Instead, our novel use of foraging paradigms, in addition to our inclusion of types of effort that are often studied separately, highlighted task-specific attributes contributing to the attractive or aversive nature of demands. The fact that predicted stable preferences for cognitive effort carried over onto the beginning of the within-subjects experiment further supported a task-specific modulation. However, the unexpected gradual convergence in acceptances in the second experiment emphasized that these features could be contextually molded.

@@

  It is possible that participants gravitated towards cognitive demands because the task configuration was not effortful. This could be due to differences in how we calibrated cognitive and physical tasks. For physical demands, we adjusted the gripping threshold to people's maximum strength, whereas we trained participants in the cognitive tasks until they reached criterion. Training might have improved response automaticity and reduce error-related risk. In addition, attributes such as the efficacy to complete a task, or the diversity of its components, have been reported to promote engagement [@Bandura2010; @Grahek2020; eisenberger]. Even so, we believe our manipulations were successful in inducing feelings of effort. Hand grips are regularly used to probe physical effort [@Chong2017; @Hogan2018; @Prevost2010], and task switching has been shown to feel cognitively effortful by recruiting cognitive control [@Kool2010; @Shenhav2017]. Furthermore, we observed a steeper decrease in acceptances over time at longer handling times, a hallmark of effortful exhertion [@Treadway2009].

@@

.

### *Points to cover*

@@

- Clinical:  Medicated patients in remission are more sensitive to effort than controls (and are not as motivated by rewards?), and this sensitivity is predictive of relapse [@Berwian2020]. Encouraging/increasing activities has been found to be a helpful treatment for depression [@Dimidjian2006]. Since depressed patients also show insensitivity to rewards [@Huys2013], identifying what makes effort appealing in its own right can help breach treatment-resistant cases. Our work suggests that subdividing a task can promote its pursual either by taxing working memory, counting, or simply distracting. Moreover, The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler). This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.

, and motivational factors affecting effort aversion can be heterogenous between depression and schizophrenia

(https://link.springer.com/chapter/10.1007%2F978-3-030-27473-3_5). Like, the aversion is due to focusing on different elements of the task. Excessive aversion to delay and effort can manifest as impulsivity and apathy, respectively [1,10–12], fluctuations in which are hallmark symptoms of various mental illnesses and substance use disorders [13]. Our findings promote the idea that motivation to exhert effort can be boosted by chopping tasks into smaller digestible chunks that don't make them feel as long. Rather than telling them the final goal, keep them busy (this should be already a thing, I'm sure...). The concavity of value means that the motivating feeling of task completion would carry more weight as pieces rather than a big net amount (thaler). This should also hold practicality for everyday scenarios, like motivating exercise, work, etc.
